\vspace{-0.25em}\thetitle

### 2009-07-17 paper.tex
...

This paper is the first in a three-part series, employing non-parametric discrete mixture modeling to understand and analyze network traffic patterns at the level of individual flows and packets.\flownote
All three papers employ the same theoretical framework but apply it to different aspects of network traffic analysis: prediction, classification and generation.
In this paper we present the framework and demonstrate how to predict detailed behavior of individual flows from the observation of only a handful of initial packets.
% The following papers will focus on classification of flows according to application type and realistic workload generation.

The fundamental concept underlying this work is that of a \emph{linear representation of network traffic}~\cite{Karpinski08}.
Linear representations operate on traffic traces at the level of flows.
A representation is a function that maps sets of flows to points in a vector space;
the space will typically have high dimension, each coordinate describing some aspect of flow behavior.
The representation must satisfy a simple linearity condition which we will describe in detail later.
% the sum of the representations of a set of flows is a vector that represents the aggregate behavior of the set of flows.
The complete behavior of a traffic trace is expressed as a matrix, where each flow in the trace is represented by a row of the matrix.

@@

The key observation of this work is that even real network traces tend to have approximately low-rank representation matrices.

>>>>

This paper is the first in a three-part series, employing non-parametric discrete mixture modeling to understand and analyze network traffic patterns at the level of individual flows and packets.\flownote
All three papers employ the same theoretical framework but investigate different fundamental applications of traffic modeling:
prediction, classification and generation.
In this paper we first present the framework and then demonstrate how it can predict detailed behavior of individual flows from the observation of only a handful of initial packets.
% The following papers will focus on classification of flows according to application type and realistic workload generation.

The fundamental concept underlying these works is \emph{linear representation of network traffic}~\cite{Karpinski08}.
A linear representation is a function that maps sets of flows to points in a vector space;
each dimension of the representation describes some aspect of flow behavior.
The representation must also satisfy a simple linearity condition which we will describe in detail later.
% the sum of the representations of a set of flows is a vector that represents the aggregate behavior of the set of flows.
An entire traffic trace may be represented as a matrix:
each flow is mapped to a row of the matrix.

@@

The key observation of this work is that real-world network traces tend to have approximately low-rank representation matrices.
